ET bias

### 2015-10-18 Rmd/et-bias.Rmd
18/10/2015, second commit, ET updated. See changelog

## Calculate bias statistics

### Mean percent bias in ET estimates
```{r, eval=FALSE}
lev_vec <- "f25"
# create mask for non-cropland areas, unioning GTI and each LC, filtering out
# areas of no-cropland (<1/2% total cover)
lcu <- lapply(lev_vec, function(x) {
  lcb <- lapply(snms, function(y) {
    gti_gt0 <- Which(round(gti_agg[[x]]$gti * 100) > 0)
    lc_gt0 <- Which(round(lc_agg[[x]][[y]] * 100) > 0)
    all_gt0 <- gti_gt0 + lc_gt0
    all_gt0[all_gt0 > 0] <- 1
    all_gt0
  })
  named_out(lcb, snms)
})
names(lcu) <- lev_vec

@@

# weighted mean functions
wm <- function(x, w) stats::weighted.mean(x, w)
wma <- function(x, w) stats::weighted.mean(abs(x), w)

@@

# reshape
mus <- rbindlist(lapply(names(mu), function(x) cbind(x, mu[[x]])))
mus[, ol := NULL]
setnames(mus, c("x", "il", "bias"), c("Variable", "Map", "Bias"))
setkeyv(mus, c("Map", "Variable"))
muas <- rbindlist(lapply(names(mua), function(x) cbind(x, mua[[x]])))
muas[, ol := NULL]
setnames(muas, c("x", "il", "bias"), c("Variable", "Map", "Abs Bias"))
setkeyv(muas, c("Map", "Variable"))
mutab <- mus[muas]
mutab[, lapply(.SD, function(x) max(abs(x))), .SDcols = 3:4]
setkey(mutab, "Variable")
vnmr <- c("Annual Mean", "29-year Max", "29-year Min", "Peak")
for(i in 1:length(vnms)) mutab[Variable == vnms[i], Variable := vnmr[i]]
setkey(mutab, "Map")
for(i in 1:length(snms)) mutab[Map == snms[i], Map := mcap[i]]
mutab[order(-rank(Map))]

>>>>

## Calculate bias/accuracy statistics

### Primary method

Density dependent method

```{r, eval=FALSE}
# weighted mean functions
wm <- function(x, w) stats::weighted.mean(x, w)
wma <- function(x, w) stats::weighted.mean(abs(x), w)
snms <- c("sa30", "globmu", "modmu", "geow")

# Quick look at density dependent
# reshape for ET mu
err2011 <- lapply("f25", function(x) {
  sapply(l2dag$mu, function(y) list(y[[x]]))
})
names(err2011) <- "f25"

# calculate bias/MAE for data 
a <- bias_statsw(gti_agg$f25, awgts, err2011$f25, snms, wm, "mu")
b <- bias_statsw(gti_agg$f25, awgts, err2011$f25, snms, wma, "mua")
et_muw <- rbind(a, b)

# reshape for ET mu
err2011 <- lapply("f25", function(x) {
  sapply(l2dag$gs, function(y) list(y[[x]]))
})
names(err2011) <- "f25"

# calculate bias/MAE for data
a <- bias_statsw(gti_agg$f25, awgts, err2011$f25, snms, wm, "mu")
b <- bias_statsw(gti_agg$f25, awgts, err2011$f25, snms, wma, "mua")
et_gsw <- rbind(a, b)
```

Agricultural area method
```{r, eval=FALSE}
lev_vec <- "f25"
# create mask for non-cropland areas, unioning GTI and each LC, filtering out
# areas of no-cropland (<1/2% total cover)
lcu <- lapply(lev_vec, function(x) {
  lcb <- lapply(snms, function(y) {
    gti_gt0 <- Which(round(gti_agg[[x]]$gti * 100) > 0)
    lc_gt0 <- Which(round(lc_agg[[x]][[y]] * 100) > 0)
    all_gt0 <- gti_gt0 + lc_gt0
    all_gt0[all_gt0 > 0] <- 1
    all_gt0
  })
  named_out(lcb, snms)
})
names(lcu) <- lev_vec

@@

@@

# reshape
mus <- rbindlist(lapply(names(mu), function(x) cbind(x, mu[[x]])))
mus[, ol := NULL]
setnames(mus, c("x", "il", "bias"), c("Variable", "Map", "Bias"))
setkeyv(mus, c("Map", "Variable"))
muas <- rbindlist(lapply(names(mua), function(x) cbind(x, mua[[x]])))
muas[, ol := NULL]
setnames(muas, c("x", "il", "bias"), c("Variable", "Map", "MAE"))
setkeyv(muas, c("Map", "Variable"))
mutab <- mus[muas]
mutab[, lapply(.SD, function(x) max(abs(x))), .SDcols = 3:4]
setkey(mutab, "Variable")
vnmr <- c("Annual Mean", "29-year Max", "29-year Min", "Peak")
for(i in 1:length(vnms)) mutab[Variable == vnms[i], Variable := vnmr[i]]
setkey(mutab, "Map")
for(i in 1:length(snms)) mutab[Map == snms[i], Map := mcap[i]]
mutab[order(-rank(Map))]
